Summary Tables

### 2021-04-14 summary_tables.Rmd
Add space
Updating summary tables before imputation

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 74.9|23.0|1.0 |
| cycle | 2.3|9.8|1.2 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.4|25.0 |

@@

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.5|10.7|1.0 |
| cycle | 7.9|11.3|2.0 |
| car | 3.5|21.6|19.7 |
| motorcycle | 1.4|7.7|6.2 |
| bus | 4.9|41.6|68.3 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 79.7|3.0|0.1 |
| cycle | 8.0|3.9|0.3 |
| car | 6.2|35.0|21.8 |
| motorcycle | 0.6|2.8|1.3 |
| bus | 3.3|49.2|50.5 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.6|6.5|0.1 |
| cycle | 3.4|4.5|0.3 |
| car | 2.2|34.9|29.7 |
| motorcycle | 0.6|4.7|1.0 |
| bus | 1.6|36.2|49.9 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 83.9|4.1|0.1 |
| cycle | 6.2|6.0|0.4 |
| car | 7.7|54.8|30.0 |
| motorcycle | 0.2|2.0|0.9 |
| bus | 0.6|21.1|30.1 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 62.2|7.2|3.0 |
| cycle | 0.7|0.9|0.3 |
| car | 22.0|45.1|29.9 |
| motorcycle | 1.3|2.9|3.8 |
| bus | 13.3|39.2|32.7 |

>>>>

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 75.0|23.0|1.0 |
| cycle | 2.3|9.8|1.1 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|25.0 |

@@

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 91.0|20.9|1.2 |
| cycle | 4.9|12.1|2.0 |
| car | 1.5|26.7|29.3 |
| motorcycle | 0.5|5.9|6.5 |
| bus | 0.8|20.7|56.8 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.2|2.9|0.1 |
| cycle | 7.4|3.6|0.3 |
| car | 6.2|34.5|21.4 |
| motorcycle | 0.6|2.8|1.2 |
| bus | 3.5|50.1|51.0 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.9|3.5|0.0 |
| cycle | 2.5|3.2|0.2 |
| car | 2.2|37.9|31.8 |
| motorcycle | 0.4|3.2|0.9 |
| bus | 1.7|34.8|33.8 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|3.9|0.0 |
| cycle | 6.2|6.1|0.5 |
| car | 8.1|58.7|32.3 |
| motorcycle | 0.1|2.2|1.1 |
| bus | 0.5|20.5|28.8 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 82.7|1.9|0.0 |
| cycle | 1.3|1.4|0.1 |
| car | 12.6|65.4|37.0 |
| motorcycle | 0.8|3.2|1.9 |
| bus | 1.0|21.3|28.9 |
